Requirements and Current State of Knowledge Representation Systems for Service Robotics

### 2012-05-10 krs-survey.tex
Updated biblio + small change in knowledge instantiation

Table~\ref{table|upper_onto_metrics} gives such metrics for four major
upper-ontologies commonly used in the semantic Web community.

\fxwarning{Add metrics for SUMO, OpenCyc, ResearchCyc}

@@

\begin{tabular}{llllll}
\toprule
{\bf Project} & {\bf Expressiveness} & {\bf Axioms} & {\bf Classes} & {\bf Properties} & {\bf Instances} \\
\midrule
OpenCyc \\
ResearchCyc \\
SUMO \\
DBPedia \\
\bottomrule

>>>>

Table~\ref{table|upper_onto_metrics} gives such metrics for four major
upper-ontologies commonly used in the semantic Web community (taken
from~\cite{Mascardi2007} and the projects' respective websites).

@@

\begin{tabular}{llllll}
\toprule
{\bf Project} & {\bf Terms} & {\bf Assertions} \\
\midrule
Cyc & > 300 000 & > 3 000 000 & \\
YAGO & > 10 000 000 & > 120 000 000 \\
SUMO & 20 000 & 60 000 \\
DBPedia (for English) & 1 840 000 & 385 000 000\\
OpenMind Common Sense (for English) & & 1 000 000\\
\bottomrule
